Explanatory Data Analysis of Trade Statistics of Turkey

### 2018-12-19 Draft/Draft20181218.Rmd
.

---
title: "Explanatory Data Analysis of Trade Statistics of Turkey"
subtitle: "MEF University - BDA 503 Essentials of Data Analytics - Fall 2018 - Group Fou\\*R* Term Project"
date: "December 2018"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    df_print: paged
    code_folding: hide
    theme: journal
    #highlight: tango

>>>>

---
title: "Explanatory Data Analysis of Trade Statistics of Turkey"
subtitle: "MEF University - BDA 503 Essentials of Data Analytics - Fall 2018 - Group Fou\\*R* Term Project"
date: "December 2018"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: false
    df_print: paged
    code_folding: hide
    theme: journal
    #highlight: tango
